On the Construction of a Collision-Free Schedule of Beacons in a Wireless Multi-Hop Network

### 2013-10-04 paper.tex
added Cristina s paper

@@

Decentralized Constraint Satisfaction \cite{} is a promising alternative to address the problem.
The constraints are that no pair of nodes connected by an arc in the interference graph should use the same color.

@@

Each station picks a random position in the schedule.
If it receives confirmation from all of its neighbors, it assumes that no collisions have occurred and keeps transmitting at that position.
Otherwise

@@

The authors would like to thank Victor Dalmau and Luis Sanabria for their helpful comments.

>>>>

\section{Related Work}
\cite{cano2013iri}

@@

In order to solve this problem in a decentralized way, we need that the nodes keep trying different colours until a solution is found.
To be more specific, a node will pick the same color if none of its neighbours has picked that particular color.
Otherwise it will change the color.

@@

Each station picks a random position in the schedule.
If it receives confirmation from all of its neighbors, it assumes that no collisions have occurred and keeps transmitting at that position.
This means that no other neighbor in the two-hop neighborhood has picked the same color.

If a node in the two-node neighborhood pick the same color, the node that is a common neighbor of both will not receive the beacon and therefore will not confirm the correct reception.

@@

The authors would like to thank ...
